---
title: "Cultural Ratchet Data Exploration"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(reshape2)
library(purrr)
library(jsonlite)
library(tidyr) 
library(dplyr)
library(tidyboot)
library(ggplot2)
library(scales)
library(readr)
library(stringr)
library(digest)
library(ggthemes)
library(forcats)
library(ggalt)
library(grid)
library(cowplot)
library(brms)
```


# Complete Games
# Uploads the game data
```{r}
# Load Test Trial Responses for Three Beakers
temp <- list.files(
  "../../data/mp-game-6/logTest",
  pattern="*.csv",
  full.names=TRUE
)
three_beaker_games <- do.call(rbind, lapply(temp, read_tsv))

accuracy_by_game <- three_beaker_games %>%
  group_by(gameid,round_num,role) %>%
  summarise(mean_accuracy = mean(is_correct)) %>%
  mutate(role = paste0(role, "_accuracy")) %>%
  spread(role, mean_accuracy)

accuracy_by_game

cor_three_beakers <- cor.test(accuracy_by_game$student_accuracy, accuracy_by_game$explorer_accuracy)

three_beaker_graph <- accuracy_by_game %>%
  ggplot(aes(x = student_accuracy, y = explorer_accuracy)) +
  geom_point(aes(color = factor(round_num)), position = position_jitter(width = .015, height = .015)) +
  geom_smooth(method = "lm") +
  theme_cowplot() + 
  labs(title = "Student vs Teacher Accuracy", subtitle = "(n = 14) p***", x = "Student Accuracy", y = "Teacher Accuracy", color = "Round") +
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") +
  xlim(0,1.05) + 
  ylim(0,1.05)

three_beaker_graph

```

#Load for four / five beaker games
```{r}
temp <- list.files(
  "../../data/mp-game-6/logTest",
  pattern="*.csv",
  full.names=TRUE
)
multi_beaker_games <- do.call(rbind, lapply(temp, read_tsv))

accuracy_by_game_multi <- multi_beaker_games %>%
  group_by(gameid,round_num,role) %>%
  summarise(mean_accuracy = mean(is_correct)) %>%
  mutate(role = paste0(role, "_accuracy")) %>%
  spread(role, mean_accuracy)

cor_multi_beakers <- cor.test(accuracy_by_game_multi$student_accuracy, accuracy_by_game_multi$explorer_accuracy)

accuracy_by_game_multi %>%
  ggplot(aes(x = student_accuracy, y = explorer_accuracy)) +
  geom_point(mapping = aes(color = factor(round_num)), position = position_jitter(width = .01, height = .01)) +
  geom_smooth(method = "lm") +
  theme_cowplot() + 
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") + 
  labs(title = "Student vs Teacher Accuracy", subtitle = "Second Iteration (n = 7)", x = "Student Accuracy", y = "Teacher Accuracy", color = "Round") + 
  xlim(0, 1.01) + 
  ylim(0, 1.01)
```

```{r}
  ggplot(NULL) +
  geom_point(data = accuracy_by_game, mapping = aes(color = "#CC0000", x = student_accuracy, y = explorer_accuracy, shape = factor(round_num)), position = position_jitter(width = .01, height = .01)) +
  geom_smooth(data = accuracy_by_game, method = "lm", aes(color = "#CC0000", x = student_accuracy, y = explorer_accuracy))  +
  labs(title = "Performance in First and Second Iterations", color = "Iteration", shape = "Round", x = "Student Accuracy", y = "Teacher Accuracy") + 
  theme_cowplot() + 
  scale_color_discrete(labels = c("#CC0000" = "First", "#000099" = "Second")) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") + 
  xlim(0, 1.05) + 
  ylim(0, 1.05)
```

```{r}

accuracy_by_round <- three_beaker_games %>%
  group_by(round_num, role) %>%
  summarise(mean_accuracy = mean(is_correct), ci_low = (mean_accuracy - 1.96*sd(is_correct)/sqrt(n())), ci_up = (mean_accuracy + 1.96*sd(is_correct)/sqrt(n()))) 

accuracy_by_round

accuracy_by_round %>%
  ggplot(aes(x = round_num, y = mean_accuracy,)) + 
  geom_col(aes(fill = factor(round_num), alpha = role), position = "dodge") + 
  geom_errorbar(aes(ymin=ci_low, ymax=ci_up, alpha = role,),  color="black", width=0.5, position= position_dodge(.9), show.legend = FALSE) +
  scale_alpha_manual(values = c("explorer" = 1.0, "student" = 0.7), labels = c("explorer" = "Teacher", "student" = "Student")) +
  guides(fill = FALSE) + 
  theme_cowplot() + 
  labs(title = "Teacher and Student Accuracies across rounds", subtitle = "First Iteration (n = 5)", x = "Round", y = "Mean Accuracy", alpha = "Role")
  
```


```{r}
accuracy_by_question_type <- three_beaker_games %>%
  group_by(round_num, fixed) %>%
  summarise(mean_accuracy = mean(is_correct), ci_low = (mean_accuracy - 1.96*sd(is_correct)/sqrt(n())), ci_up = (mean_accuracy + 1.96*sd(is_correct)/sqrt(n()))) 

accuracy_by_question_type

accuracy_by_question_type %>%
  ggplot() + 
  geom_col(aes(x = round_num, y = mean_accuracy, fill = factor(round_num), alpha = fixed), position = "dodge") + 
  scale_alpha_manual(values = c("beaker" = 1.0, "reaction" = 0.4), labels = c("beaker" = "Forward", "reaction" = "Backward")) +
  geom_errorbar(aes(x = round_num,ymin=ci_low, ymax=ci_up, alpha = fixed,),  color="black", width=0.5, position= position_dodge(.9), show.legend = FALSE) +
  scale_color_manual(values = c("reaction" = "black", "beaker" = "black"), labels = c("reaction" = "Backward", "beaker" = "Forward")) +
  guides(fill = FALSE) + 
  theme_cowplot() + 
labs(title = "Accuracies across Question Type", subtitle = "First Iteration (n = 5)", x = "Round", y = "Mean Accuracy", alpha = "Question Type", color = "Chance Accuracy")
  
```


```{r}
all_games <- three_beaker_games

all_games

accuracy_by_question_multi <- three_beaker_games %>%
  group_by(round_num, fixed, config, role)  %>%
  summarise(mean_accuracy = mean(is_correct), ci_low = (mean_accuracy - 1.96*sd(is_correct)/sqrt(n())), ci_up = (mean_accuracy + 1.96*sd(is_correct)/sqrt(n())), chance_accuracy = .125) %>%
  filter(round_num == 0, fixed == "reaction")

accuracy_by_question_multi

accuracy_by_question_multi %>%
  ggplot() + 
  geom_col(aes(x = config, y = mean_accuracy, fill = fixed, alpha = role), position = "dodge") + 
  scale_alpha_manual(values = c("explorer" = 1.0, "student" = 0.4)) +
  geom_errorbar(aes(x = config, ymin=ci_low, ymax=ci_up, alpha = role,),  color="black", width=0.5, position= position_dodge(.9), show.legend = FALSE) +
  guides(fill = FALSE) + 
  theme_cowplot() + 
labs(title = "Accuracies across Question Type", subtitle = "First Iteration (n = 5)", x = "Round", y = "Mean Accuracy", alpha = "Question Type")

accuracy_by_question_multi
  
```

```{r}
accuracy_by_question <- three_beaker_games %>%
  group_by(round_num, fixed, config, role) %>%
  summarise(chance_accuracy = mean((str_count(true_answers, ",") + 1)/8) , mean_accuracy = mean(is_correct), ci_low = (mean_accuracy - 1.96*sd(is_correct)/sqrt(n())), ci_up = (mean_accuracy + 1.96*sd(is_correct)/sqrt(n()))) %>%
  filter(round_num == 0, fixed == "reaction")

accuracy_by_question

accuracy_by_question_manip <- accuracy_by_question %>%
  mutate(role = paste0(role, "_accuracy")) %>%
  select(-ci_low, -ci_up) %>%
  spread(role, mean_accuracy)
  
#cor_questions <- cor.test(accuracy_by_question_manip$student_accuracy, accuracy_by_question_manip$explorer_accuracy)

accuracy_by_question %>%
  ggplot() + 
  geom_col(aes(x = config, y = mean_accuracy, alpha = role), position = "dodge", fill = "plum4") + 
  scale_alpha_manual(values = c("explorer" = 1.0, "student" = 0.7), labels = c("explorer" = "Teacher", "student"= "Student")) +
  geom_errorbar(aes(x = config, ymin=ci_low, ymax=ci_up, alpha = role),  color="black", width=0.5, position= position_dodge(.9), show.legend = FALSE) +
  geom_col(aes(x = config, y = chance_accuracy, color = fixed), fill = "purple", alpha = .1, position = "dodge")+
  guides(fill = FALSE) + 
  scale_color_manual(values = c("reaction" = "blue", "beaker" = "purple"), labels = c("reaction" = "Chance Accuracy", "beaker" = "Chance Accuracy")) + 
  theme_cowplot() + 
labs(title = "Student and Teacher against Chance Accuracy", subtitle = "Round 1", x = "Question", y = "Mean Accuracy", color = "", alpha = "Role")
  
```



```{r}
temp <- list.files(
  "../../data/mp-game-6/logSimpleTimes",
  pattern="*.csv",
  full.names=TRUE
)
game_times <- do.call(rbind, lapply(temp, read_tsv))
game_train_times <- game_times %>%
  filter(role == "explorer") %>%
  select(-logTime, -experimentName, -iterationName, -eventType)
all_accuracies_by_game <- rbind(accuracy_by_game)
game_times_and_accuracies <- merge(game_train_times, all_accuracies_by_game, by =c("gameid", "round_num"))

game_train_times

cor_times <- cor.test(game_times_and_accuracies$`Total Train Time`, game_times_and_accuracies$explorer_accuracy)

cor_times

game_times_and_accuracies %>%
  ggplot(aes(x = `Total Train Time`, y = explorer_accuracy)) + 
  geom_point(aes(color = factor(round_num))) + 
  geom_smooth(method = "lm") + 
  theme_cowplot() + 
  labs(title = "Train Time vs Explorer Accuracy", subtitle = "(n = 14) p = .0075", color = "Round", y = "Teacher Accuracy", 
       x = "Train Time (s)") 


```

```{r}

game_times_split <- game_times %>%
  gather(Type, Time, c(`Total Train Time`, `Total Test Time`, chat)) %>%
  group_by(Type) %>%
  summarise(average_time = mean(Time), ci_low = (average_time - 1.96*sd(Time)/sqrt(n())), ci_up = (average_time + 1.96*sd(Time)/sqrt(n())), lang = "(n = 14)")

game_times_split_all <- rbind(game_times_split) %>%
  filter(Type != "Total Test Time") %>%
  mutate(Type = ifelse(Type == "chat", "Typing", Type), Type = ifelse(Type == "Total Train Time", "Experimenting", Type))

game_times_split_all

game_times_split_all %>%
  ggplot() + 
  geom_col(aes(x = lang, y = average_time, fill = lang, alpha = Type), position = "dodge") + 
  geom_errorbar(aes(x = lang, ymin=ci_low, ymax=ci_up, fill = lang, alpha = Type),  color="black", width=0.5, position = position_dodge(.9), show.legend = FALSE) +
  scale_alpha_manual(values = c("Typing" = 0.6, "Experimenting" = 1.0)) +
  theme_cowplot() + 
  labs(title = "Time spent learning vs teaching", subtitle = "(n = 14)", x = "Language Type", y = "Mean Time (s)", fill = "Language Type", alpha = "Task") +
  guides(fill = FALSE)

```

```{r}
temp <- list.files(
  "../../data/mp-game-6/logSimpleTimes/Brute",
  pattern="*.csv",
  full.names=TRUE
)
game_times_brute <- do.call(rbind, lapply(temp, read_tsv))

temp <- list.files(
  "../../data/mp-game-6/logSimpleTimes/Causal",
  pattern="*.csv",
  full.names=TRUE
)
game_times_causal <- do.call(rbind, lapply(temp, read_tsv))

game_times_split_brute <- game_times_brute %>%
  gather(Type, Time, c(`Total Train Time`, `Total Test Time`, chat)) %>%
  group_by(Type) %>%
  summarise(average_time = mean(Time), ci_low = (average_time - 1.96*sd(Time)/sqrt(n())), ci_up = (average_time + 1.96*sd(Time)/sqrt(n())), lang = "Brute (n = 4)")

game_times_split_causal <- game_times_causal %>%
  gather(Type, Time, c(`Total Train Time`, `Total Test Time`, chat)) %>%
  group_by(Type) %>%
  summarise(average_time = mean(Time), ci_low = (average_time - 1.96*sd(Time)/sqrt(n())), ci_up = (average_time + 1.96*sd(Time)/sqrt(n())), lang = "Causal (n = 10)")

game_times_split_all <- rbind(game_times_split_brute, game_times_split_causal) %>%
  filter(Type != "Total Test Time") %>%
  mutate(Type = ifelse(Type == "chat", "Student", Type), Type = ifelse(Type == "Total Train Time", "Teacher", Type))

game_times_split_all

game_times_split_all %>%
  ggplot() + 
  geom_col(aes(x = lang, y = average_time, fill = lang, alpha = Type), position = "dodge") + 
  geom_errorbar(aes(x = lang, ymin=ci_low, ymax=ci_up, fill = lang, alpha = Type),  color="black", width=0.5, position = position_dodge(.9), show.legend = FALSE) +
  scale_alpha_manual(values = c("Student" = 0.6, "Teacher" = 1.0)) +
  theme_cowplot() + 
  labs(title = "Time spent learning vs teaching", subtitle = "(n = 14)", x = "Language Type", y = "Mean Time (s)", fill = "Language Type", alpha = "Task") +
  guides(fill = FALSE)

```





```{r}
accuracy_by_question_by_role <- three_beaker_games %>%
  group_by(round_num, fixed, config, role) %>%
  summarise(mean_accuracy = mean(is_correct)) %>%
  mutate(role = paste0(role, "_accuracy")) %>%
  spread(role, mean_accuracy)

accuracy_by_question_by_role

  
cor_questions <- cor.test(accuracy_by_question_by_role$student_accuracy, accuracy_by_question_by_role$explorer_accuracy)

cor_questions

accuracy_by_question_by_role %>%
  ggplot(aes(x = student_accuracy, y = explorer_accuracy)) + 
  geom_point(aes(color = fixed), position = position_jitter(width = .01, height = .01)) + 
  geom_smooth(method = "lm", color = "seagreen") +
  scale_color_manual(values = c("beaker" = "slateblue", "reaction" = "indianred"),labels = c("beaker" = "Forward", "reaction" = "Backward")) + 
  theme_cowplot() + 
   labs(title = "Student vs Teacher Accuracy by Question", subtitle = "Both Iterations (n = 14) p***", color = "Question Type", x = "Student Accuracy", y = "Teacher Accuracy") +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  xlim(0,1.05) + 
  ylim(0,1.05)

```

```{r}
# Generate agreement data

# Gather the data together - have teacher and student accuracy for each question
agreement <- three_beaker_games %>%
  group_by(round_num, fixed, config, gameid) %>%
  select(-iterationName, -experimentName, -eventType, -time, -turker_answer, -true_answers) %>%
  spread(role, is_correct) 

#Calculate the average agreement for each game in each round
agreement_by_question <- agreement %>%
  summarise(agreement = identical(explorer, student)) %>%
  group_by(gameid, fixed, round_num) %>%
  summarise(mean_agreement = mean(agreement), type = "actual_agreement") 

#Calculate the accuracies for each game in each round / question type
accuracy_by_round_game <- three_beaker_games %>%
  group_by(gameid,round_num, fixed, role) %>%
  summarise(mean_accuracy = mean(is_correct)) %>%
  mutate(role = paste0(role, "_accuracy")) %>%
  spread(role, mean_accuracy)

# From above accuracies, calculate the random expected agreement for each round / question type
random_agreement_by_round_game <- accuracy_by_round_game %>%
  summarise(mean_agreement = (explorer_accuracy*student_accuracy + (1-explorer_accuracy)*(1-student_accuracy)), type = "chance_agreement") 

#Combine actual and chance agreements
agreement_by_round_game <- rbind(agreement_by_question, random_agreement_by_round_game) %>%
  spread(type, mean_agreement)

#Calculate average random and actual agreement for each round across all games
agreement_by_round <- agreement_by_round_game %>%
  group_by(fixed, round_num) %>%
  summarise(mean_actual_agreement = mean(actual_agreement), mean_chance_agreement = mean(chance_agreement)) 


```

```{r}

#Agreement Graphs

#Change to binary values for graphing
agreement <- agreement %>%
  mutate(explorer = as.numeric(explorer), student = as.numeric(student))

#Calculate correlations

cor_agreement <- cor.test(agreement$student, agreement$explorer)

cor_chance_agreement <- cor.test(agreement_by_round_game$chance_agreement, agreement_by_round_game$actual_agreement)

agreement %>%
  ggplot(aes(x = student, y = explorer)) +
  geom_point(mapping = aes(color = factor(round_num)), position = position_jitter(width = .05, height = .05)) +
  geom_smooth(method = "lm") +
  theme_cowplot() + 
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") + 
  labs(title = "Student vs Teacher Question Accuracy", subtitle = "(n = 14), p***", x = "Student Accuracy", y = "Teacher Accuracy", color = "Round") + 
  xlim(-.05, 1.2) + 
  ylim(-.05, 1.2)


#Scatter plot of individual game rounds, average vs real agreement
agreement_by_round_game %>%
  ggplot(aes(x = chance_agreement, y = actual_agreement)) +
  geom_point(mapping = aes(color = factor(round_num), shape = fixed), position = position_jitter(width = .02, height = .02)) +
  geom_smooth(method = "lm") +
  theme_cowplot() + 
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") + 
  labs(title = "Chance vs Actual Agreement", subtitle = "(n = 14), p***", x = "Chance Agreement", y = "Actual Agreement", color = "Round", shape = "Question Type") + 
  xlim(-.05, 1.05) + 
  ylim(-.05, 1.05)

#Bar chart of average random agreement per round vs actual average agreement
agreement_by_round %>%
  ggplot() + 
  geom_col(aes(x = round_num, y = mean_actual_agreement, fill = round_num, alpha = fixed), position = "dodge") +
  scale_alpha_manual(values = c("beaker" = 0.6, "reaction" = 1.0)) +
  theme_cowplot() + 
  labs(title = "Mean Student-Teacher Agreement", subtitle = "(n = 5)", x = "Round", y = "Mean Agreement", fill = "Round", alpha = "Question Type", color = "Chance Agreement") + 
  geom_col(aes(x = round_num, y = mean_chance_agreement, color = fixed), fill = "purple", alpha = .0, position = "dodge") +
  scale_color_manual(values = c("reaction" = "black", "beaker" = "black"), labels = c("reaction" = "Backward", "beaker" = "Forward")) +
  guides(fill = FALSE)+ 
  ylim(-.05, 1.05)
  
  


```

```{r}
# Load Time Summary Stats
temp <- list.files(
    "../../data/mp-game-6/logScores",
  pattern="*.csv",
  full.names=TRUE
)
temp
scores_complete_games <- do.call(rbind, lapply(temp, read.csv, sep=""))
scores_complete_games

# Load Time Data
temp <- list.files(
    "../../data/mp-game-6/logSimpleTimes",
  pattern="*.csv",
  full.names=TRUE
)
time_complete_games <-do.call(rbind, lapply(temp, read.csv, sep="")) %>%
  group_by(gameid)
```

## Distribution of Complete Data
# Makes a plot of the number of games played by each rule_idx. Think I need to change to config code
```{r}
num_complete_games_played <- scores_complete_games %>%
  count(rule_idx) %>%
  mutate(n = n/2)

num_complete_games_played$n <- as.factor(num_complete_games_played$n)

ggplot(data=num_complete_games_played, aes(x=rule_idx, y=n)) +
  geom_bar(stat="identity") +
  labs(
    title = "Data Distribution of Complete Games",
    x = "Rule Index",
    y = "Number of Samples"
  )  +
  scale_y_discrete()
```


## Student Performance Vs. Teacher Performance 

Regression analysis

```{r regression_accuracy, eval = F}
scores_complete_games <- scores_complete_games %>%
  mutate(correct = hits + correct_rejections,
         incorrect = misses + false_alarms,
         accuracy = correct / (correct + incorrect),
         rule_type = floor(rule_idx/10),
         workerid = paste(gameid, role, sep = "_"),
         rule_fac = factor(rule_type,
                           levels = c(0, 1, 2, 3, 4),
                           labels = c("single","conj", "disj",
                                      "conjDisj", "disjConj")),
         concept_fac = factor(rule_idx),
         role = factor(role)
         )
## these "center" the predictors, to look at the effect of rule at the average of the roles
# and the effect of role at the average of the rules
contrasts(scores_complete_games$rule_fac) = contr.sum(5)
contrasts(scores_complete_games$role) = contr.sum(2)
contrasts(scores_complete_games$role)
contrasts(scores_complete_games$rule_fac) 

brm.accuracy.rs <- brm(
  data = scores_complete_games,
  formula = correct | trials(50) ~ rule_fac*role + 
    (1 + rule_fac | workerid) +
    (1 + role | concept_fac),
  family = "binomial",
  chains = 3, cores = 3
)

summary(brm.accuracy.rs)
```
```{r reg_acc_pp, eval = F}
antilogit = function(x) 1 / (1 + exp(-x))
newdata = expand.grid(rule_fac = factor(
  levels(scores_complete_games$rule_fac),
    levels = c("single","conj", "disj", "conjDisj", "disjConj")),
  role = factor(levels(scores_complete_games$role))) 
#coda = brms::posterior_samples(brm.accuracy.rs)

contrasts(newdata$rule_fac) = contr.sum(5)
contrasts(newdata$role) = contr.sum(2)
fit = fitted(brm.accuracy.rs,
             newdata = newdata,
             re_formula = NA,
             summary = TRUE)


df_plot = cbind(newdata, fit)

fit1 = as.data.frame(fitted( brm.accuracy.rs,
                          newdata = newdata, re_formula = NA, 
                          summary = FALSE # extract the full MCMC
))

colnames(fit1) = newdata %>% 
  mutate(newcol = paste(rule_fac, role, sep = "_")) %>% 
  pull(newcol)

posterior.predictive.fit <- fit1 %>%
  mutate(stud_minus_teach = (
    (single_student - single_explorer) +
           (conj_student - conj_explorer) + 
           (disj_student - disj_explorer) + 
           (conjDisj_student - conjDisj_explorer) + 
           (disjConj_student - disjConj_explorer)
           ) / 5,
    stud_minus_teach_prob = stud_minus_teach / 50 )

quantile(posterior.predictive.fit$stud_minus_teach_prob, probs = c(.5, .025, .975))

posterior.predictive.fit %>%
  ggplot(., aes( x = stud_minus_teach_prob))+
  geom_histogram()
```

```{r}
brm.accuracy.rs.2 <- brm(
  data = scores_complete_games,
  formula = correct | trials(50) ~ rule_fac*role + 
    (1 | workerid) +
    (1 + role | concept_fac),
  family = "binomial",
  chains = 3, cores = 3
)

summary(brm.accuracy.rs.2)
contrasts(scores_complete_games$rule_fac)
```

```{r}
# Accuracies
complete_test_explorer <- scores_complete_games %>%
  filter(role == "explorer") %>%
  mutate(correct = hits + correct_rejections) %>%
  mutate(incorrect = misses + false_alarms) %>%
  select(gameid, rule_idx, correct, incorrect) %>%
  mutate(explorer_acc = correct / (correct + incorrect)) %>%
  mutate(rule_type = floor(rule_idx/10))

complete_test_student <- scores_complete_games %>%
  filter(role == "student") %>%
  mutate(correct = hits + correct_rejections) %>%
  mutate(incorrect = misses + false_alarms) %>%
  select(gameid, rule_idx, incorrect, correct) %>%
  mutate(student_acc = correct / (correct + incorrect)) %>%
  mutate(rule_type = floor(rule_idx/10))

complete_test_explorer_summary <- complete_test_explorer %>%
  group_by(rule_idx) %>%
  tidyboot_mean(column = explorer_acc) %>%
  rename(avg_explorer_acc = mean) %>%
  rename(explorer_ci_lower = ci_lower) %>%
  rename(explorer_ci_upper = ci_upper )%>%
  mutate(rule_type = floor(rule_idx/10))

complete_test_student_summary <- complete_test_student %>%
  group_by(rule_idx) %>%
  tidyboot_mean(column = student_acc) %>%
  rename(avg_student_acc = mean) %>%
  rename(student_ci_lower = ci_lower) %>%
  rename(student_ci_upper = ci_upper) %>%
  mutate(rule_type = floor(rule_idx/10))

complete_test <- bind_cols(complete_test_explorer, complete_test_student) %>%
    select(rule_idx, student_acc, explorer_acc, rule_type, gameid) 
complete_test$rule_idx <- as.factor(complete_test$rule_idx)
complete_test$rule_type <- as.factor(complete_test$rule_type)
complete_test <- complete_test %>%
  mutate(rule_type_text = fct_recode(rule_type,
    "Single Feature" = "0",
    "Conjunction" = "1",
    "Disjunction" = "2",
    "Conjunctive Disjunction" = "3",
    "Disjunctive Conjunction" = "4"
  ))

complete_test_summary <- bind_cols(complete_test_explorer_summary, complete_test_student_summary) %>% bind_cols(concept_summary) %>%
  select(rule_idx, avg_student_acc, avg_explorer_acc, student_ci_lower, student_ci_upper, explorer_ci_lower,  explorer_ci_upper, p_test_belongs_to_concept, phrase, kind, name, type, rule_type, chance_rate) %>%
  rename(student_acc = avg_student_acc) %>%
  rename(explorer_acc = avg_explorer_acc)   
complete_test_summary$rule_idx <- as.factor(complete_test_summary$rule_idx)
complete_test_summary$rule_type <- as.factor(complete_test_summary$rule_type)
complete_test_summary <- complete_test_summary %>%
  mutate(rule_type_text = fct_recode(rule_type,
    "Single Feature" = "0",
    "Conjunction" = "1",
    "Disjunction" = "2",
    "Conjunctive Disjunction" = "3",
    "Disjunctive Conjunction" = "4"
  ))

# Swap rows to make labeling cleaner

# Conjunction
x <- complete_test_summary[11:20,]
y <- x[1:8,]
z <- x[9:10,]
x[1:2,] = z
x[3:10,] = y
complete_test_summary[11:20,] = x

# Disjunction
x <- complete_test_summary[21:30,]
y <- x[1:6,]
z <- x[7:10,]
x[1:4,] = z
x[5:10,] = y
complete_test_summary[21:30,] = x


# Conjunctive Disjunction
x <- complete_test_summary[31:40,]
y <- x[1:4,]
z <- x[5:10,]
x[1:6,] = z
x[7:10,] = y
complete_test_summary[31:40,] = x


# Disjunctive Conjunction
x <- complete_test_summary[41:50,]
y <- x[1:2,]
z <- x[3:10,]
x[1:8,] = z
x[9:10,] = y
complete_test_summary[41:50,] = x

complete_test_summary <- complete_test_summary %>% mutate(id = row_number())
```

```{r}
# Individual Dyad Correlation 
cor.test(complete_test$student_acc, complete_test$explorer_acc)
```


```{r}
# Concept Type Accuracy Comparison
complete_type_summary <- scores_complete_games %>%
  mutate(
    correct = hits + correct_rejections,
    incorrect = misses + false_alarms,
    acc = correct / (correct + incorrect),
    rule_type = floor(rule_idx/10)
  ) %>%
  group_by(rule_type, role) %>%
  tidyboot_mean(column = acc)
complete_type_summary$rule_type <- as.factor(complete_type_summary$rule_type)
complete_type_summary <- complete_type_summary %>%
  mutate(rule_type_text = fct_recode(rule_type,
    "Single" = "0",
    "Conj." = "1",
    "Disj." = "2",
    "Conj. Disj." = "3",
    "Disj. Conj." = "4"
  ))
complete_type_summary$role <- as.factor(complete_type_summary$role)
complete_type_summary <- complete_type_summary %>%
  mutate(role = fct_recode(role,
    "Teacher" = "explorer",
    "Student" = "student"
  )) %>%
  rename(Role = role)

complete_type_summary$Role = factor(complete_type_summary$Role, levels = c("Teacher", "Student"))

```

```{r}
# Concept Type Average Accuracy
ggplot(
  complete_type_summary,
  aes(rule_type_text, alpha=Role, fill=rule_type_text, y=empirical_stat)
) + 
  geom_col(position='dodge', color="black") +  
  labs(
    x = "Rule",
    y = "Accuracy"
  ) + 
  geom_errorbar(aes(x=rule_type_text, ymin=ci_lower, ymax=ci_upper), color="black", width=0.5, position=position_dodge(.9), show.legend = FALSE) +
  theme_few() +
  theme(
    axis.text.x  = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title = element_text(size=15),
    legend.title = element_text(size=15),
    legend.text = element_text(size=10)
  ) +
  guides(color=FALSE) +
  guides(fill = guide_legend("Rule"), color=FALSE) +
  scale_alpha_manual(values = c("Teacher" = 1.0, "Student" = 0.2)) +
  

ggsave("./analyses/concept-type-accuracy.png", plot = last_plot(), width=5, height=3)
```

```{r regression_accuracyDiff_byConcept}
# concept specific gaps between teacher and student

complete_acc_diffs <- complete_test %>%
  mutate(diff = explorer_acc - student_acc)
  


## these "center" the predictors, to look at the effect of rule at the average of the roles
# and the effect of role at the average of the eurles
contrasts(complete_acc_diffs$rule_idx) = contr.sum(50)
contrasts(complete_acc_diffs$rule_idx) 

brm.accuracy.diff.rs <- brm(
  data = complete_acc_diffs,
  formula = diff ~ rule_idx + (1 | gameid),
  #family = "binomial",
  chains = 3, cores = 3
)


```


```{r fig.width=7, fig.height=4, echo=FALSE}
# Scatter Plot of Average Accuracies & Teacher-Student Pairs
ggplot(complete_test_summary
       , aes(x=student_acc, y=explorer_acc, fill=rule_type_text, label=rule_idx)) +
  geom_point(data = complete_test, size = 4, alpha=0.7, shape=21, show.legend=FALSE) +
  geom_point(size = 10, shape=21, color="black") +
  theme_few() +
  guides(fill = guide_legend("Rule"), color=FALSE) +
  labs(
    x = "Student Accuracy",
    y = "Teacher Acccuracy"
  ) +
  geom_abline(intercept = 0, slope = 1, linetype = 2) +
  geom_errorbar(aes(ymax = explorer_ci_lower, ymin = explorer_ci_upper), alpha=0.15) +
  geom_errorbarh(aes(xmax = student_ci_lower, xmin = student_ci_upper), alpha=0.15) +
  coord_fixed() +
  scale_x_continuous(limits = c(0.0, 1.0), breaks = c(0.25, 0.5, 0.75, 1.0)) +
  scale_y_continuous(limits = c(0.0, 1.0), breaks = c(0.25, 0.5, 0.75, 1.0)) +
  theme(text = element_text(size=20))
        
#ggsave("./analyses/accuracy_scatter_plot.png", plot = last_plot())
#   theme(
#     axis.title = element_text(size=20),
#     legend.title = element_text(size=25),
#     legend.text = element_text(size=15),
#     legend.position = c(0.7, 0.17),
#     legend.background = element_rect(fill=alpha(0.1)),
#     plot.title = element_blank()
#   )
# 
# ggsave("./analyses/accuracy_scatter_plot.png", plot = last_plot(), width=9, height=9)
```


```{r fig.width=7, fig.height=4, echo=FALSE}
ggplot(complete_test_summary, aes(x=explorer_acc, xend=student_acc, y=reorder(id, desc(id)))) + 
  theme_few() +
  geom_dumbbell(
    size=0,
    size_x=4,
    size_xend = 4,
    colour_x="black",
    colour_xend = "gray", show.legend = T) +
    labs(
      x="Accuracy"
    ) +
  geom_segment(
    aes(
      color=rule_type_text,
      x=explorer_acc, 
      xend=student_acc, 
      y=reorder(id, desc(id)), 
      yend=reorder(id, desc(id))),
    size=2) +
  guides(color = guide_legend("Rule Type")) +
  geom_point(aes(x=chance_rate, y=reorder(id, desc(id)), shape=15), size=4, inherit.aes=F, show.legend = F, color="orange") +
  scale_shape_identity() + 
  scale_x_continuous(breaks = c(0.25, 0.5, 0.75, 1.0)) + 
  scale_y_discrete(labels = rev(c(
    "flowers: orange stems",
    "flowers: thorns present",
    "fish: white fangs",
    "fish: whiskers present",
    "bugs: orange head",
    "bugs: no wings",
    "birds: tail present",
    "birds: purple tail",
    "trees: purple berries",
    "trees: no leaves",

    "flowers: purple stem AND thorn",
    "flowers: orange petals AND purple center",
    "fish: white stripes AND whiskers  present",
    "fish: orange bodies AND purple stripe",
    "bugs: purple legs AND white head",
    "bugs: wings AND antennae present",
    "birds: purple wings AND crest present",
    "birds: orange wings AND tail present",
    "trees: orange trunk AND berries present",
    "trees: purple leaves AND berries present",

    "flowers: purple petals OR thorns present",
    "flowers: orange stems OR thorns present",
    "fish: orange bodies OR fangs present",
    "fish: white stripes OR whiskers present",
    "bugs: orange antennae OR wings present",
    "bugs: purple wings OR white legs",
    "birds: orange tail OR white wings",
    "birds: orange crest OR purple wings",
    "trees: purple berries OR white trunk",
    "trees: white leaves OR orange berries",

    "flowers: (purple stem AND white petals) OR orange center",
    "flowers: (thorns present AND purple petals) OR orange stem",
    "fish: (orange body AND purple stripes) OR whiskers present",
    "fish: (white body AND orange stripes) OR fangs present",
    "bugs: (purple legs AND white head) OR orange wings",
    "bugs: (white legs AND purple wings) OR orange antennae",
    "birds: (purple wings AND white crest) OR white tail",
    "birds: (purple crest AND purple tail) OR orange wings",
    "trees: (orange berries AND purple trunks) OR white leaves",
    "trees: (leaves present AND berries present) OR orange trunks",

    "flowers: (purple center OR orange stem) AND thorns present",
    "flowers: (purple stem OR thorns present) AND white center",
    "fish: (orange body OR fangs present) AND whiskers present",
    "fish: (white stripes OR purple body) AND whiskers present",
    "bugs: (antennae present OR wings present) AND purple body",
    "bugs: (white head OR orange antennae) AND purple legs",
    "birds: (orange tail OR white wings) AND orange crest",
    "birds: (white crest OR orange wings) AND tail present",
    "trees: (purple trunks OR white leaves) AND orange berries",
    "trees: (orange trunks OR berries present) AND white leaves"
  ))
) +
  coord_cartesian(xlim=c(0.45, 1.0)) +
  theme(text = element_text(size=13))

#ggsave("./analyses/accuracy_base_rate_plot.png", plot = last_plot(), width = 14, height = 8, dpi = 300, )
```

## Concept Type Accuracy Comparison
```{r}
complete_type_summary <- scores_complete_games %>%
  mutate(
    correct = hits + correct_rejections,
    incorrect = misses + false_alarms,
    acc = correct / (correct + incorrect),
    rule_type = floor(rule_idx/10)
  ) %>%
  group_by(rule_type, role) %>%
  tidyboot_mean(column = acc)
complete_type_summary$rule_type <- as.factor(complete_type_summary$rule_type)
complete_type_summary <- complete_type_summary %>%
  mutate(rule_type_text = fct_recode(rule_type,
    "Single" = "0",
    "Conj." = "1",
    "Disj." = "2",
    "Conj. Disj." = "3",
    "Disj. Conj." = "4"
  ))
complete_type_summary$role <- as.factor(complete_type_summary$role)
complete_type_summary <- complete_type_summary %>%
  mutate(role = fct_recode(role,
    "Teacher" = "explorer",
    "Student" = "student"
  )) %>%
  rename(Role = role)

  
```

```{r}
ggplot(complete_type_summary, aes(rule_type_text, fill=Role, y=empirical_stat)) + 
  geom_col(position='dodge') +  
  labs(
    title = "Concept Type vs. Participant Accuracy",
    x = "Concept Type",
    y = "Accuracy %"
  ) + 
  geom_errorbar(aes(x=rule_type_text, ymin=ci_lower, ymax=ci_upper), color="black", width=0.5, position=position_dodge(.9)) +
  theme_few()
#ggsave("concept-type-accuracy.png", plot = last_plot())
```

## Hits, Misses, False Alarms, Correct Rejections Breakdown (Proportion)
```{r}
complete_test_perf_breakdown <- scores_complete_games %>%
  select(role, rule_idx, hits, misses, correct_rejections, false_alarms) %>%
  group_by(role, rule_idx) %>% 
  summarise_all(sum) %>%
  mutate(rule_type = floor(rule_idx/10))

complete_test_perf_breakdown$rule_idx <- as.factor(complete_test_perf_breakdown$rule_idx)
complete_test_perf_breakdown$rule_type <- as.factor(complete_test_perf_breakdown$rule_type)
complete_test_perf_breakdown <- complete_test_perf_breakdown %>%
  mutate(rule_type_text = 
           fct_recode(rule_type,
              "Single Feature" = "0",
              "Conjunction" = "1",
              "Disjunction" = "2",
              "Conjunctive Disjunction" = "3",
              "Disjunctive Conjunction" = "4",
            ),
        rule_idx_text = 
          fct_recode(rule_idx,
            "flowers: orange stems" = "0",
            "flowers: thorns present" = "1",
            "fish: white fangs" = "2",
            "fish: whiskers present" = "3",
            "bugs: orange head" = "4",
            "bugs: no wings" = "5",
            "birds: tail present" = "6",
            "birds: purple tail" = "7",
            "trees: purple berries" = "8",
            "trees: no leaves" = "9",
        
            "flowers: purple stem AND thorn" = "10",
            "flowers: orange petals AND purple center" = "11",
            "fish: white stripes AND whiskers  present"= "12" ,
            "fish: orange bodies AND purple stripe" = "13",
            "bugs: purple legs AND white head" = "14",
            "bugs: wings AND antennae present" = "15",
            "birds: purple wings AND crest present" = "16",
            "birds: orange wings AND tail present" = "17",
            "trees: orange trunk AND berries present" = "18",
            "trees: purple leaves AND berries present"= "19",
        
            "flowers: purple petals OR thorns present" = "20",
            "flowers: orange stems OR thorns present" = "21",
            "fish: orange bodies OR fangs present" = "22",
            "fish: white stripes OR whiskers present" = "23",
            "bugs: orange antennae OR wings present" = "24",
            "bugs: purple wings OR white legs" = "25",
            "birds: orange tail OR white wings" = "26",
            "birds: orange crest OR purple wings" = "27",
            "trees: purple berries OR white trunk" = "28",
            "trees: white leaves OR orange berries" = "29",
        
            "flowers: (purple stem AND white petals) OR orange center" = "30",
            "flowers: (thorns present AND purple petals) OR orange stem" = "31",
            "fish: (orange body AND purple stripes) OR whiskers present" = "32",
            "fish: (white body AND orange stripes) OR fangs present" = "33",
            "bugs: (purple legs AND white head) OR orange wings" = "34",
            "bugs: (white legs AND purple wings) OR orange antennae" = "35",
            "birds: (purple wings AND white crest) OR white tail" = "36",
            "birds: (purple crest AND purple tail) OR orange wings" = "37",
            "trees: (orange berries AND purple trunks) OR white leaves" = "38",
            "trees: (leaves present AND berries present) OR orange trunks" = "39",
        
            "flowers: (purple center OR orange stem) AND thorns present" = "40",
            "flowers: (purple stem OR thorns present) AND white center" = "41",
            "fish: (orange body OR fangs present) AND whiskers present" = "42",
            "fish: (white stripes OR purple body) AND whiskers present" = "43",
            "bugs: (antennae present OR wings present) AND purple body" = "44",
            "bugs: (white head OR orange antennae) AND purple legs" = "45",
            "birds: (orange tail OR white wings) AND orange crest" = "46",
            "birds: (white crest OR orange wings) AND tail present" = "47",
            "trees: (purple trunks OR white leaves) AND orange berries" = "48",
            "trees: (orange trunks OR berries present) AND white leaves" = "49")
)

complete_test_perf_breakdown_melted <- complete_test_perf_breakdown %>%
  melt(measure.vars = c("hits", "misses", "correct_rejections", "false_alarms"))

complete_test_perf_sums <- complete_test_perf_breakdown_melted %>%
  group_by(rule_idx, rule_type, rule_type_text, rule_idx_text, role) %>%
  summarise(norm_constant = sum(value))

complete_test_perf_breakdown_normalized <- complete_test_perf_breakdown_melted %>% 
  inner_join(., complete_test_perf_sums) %>%
  mutate(value = value/norm_constant) %>%
  select(rule_idx, rule_type, rule_type_text, rule_idx_text, value, role, variable)
```

## Hits, Misses, False Alarms, Correct Rejections Breakdown (Proportions)
```{r fig.width=10, fig.height=10, echo=FALSE}
ggplot(complete_test_perf_breakdown_normalized, aes(x = reorder(role, desc(role)), y = value, fill = variable)) + 
  geom_bar(stat = 'identity', position = 'stack') + facet_wrap(rule_idx_text ~ rule_type_text, ncol=10,  labeller = label_wrap_gen(width=30)) +
    labs(
      title = "Teacher & Student Performance Across Concept Rules",
      y = "Proportions"
  theme(
    axis.title = element_text(size=20),
    legend.title = element_text(size=25),
    legend.text = element_text(size=15),
    plot.title = element_blank(),
    axis.title.y = element_blank(),
    axis.text.x = element_text(size=15)
  )
ggsave("./analyses/accuracy_base_rate_plot.png", plot = last_plot(), width = 14, height = 8, dpi = 300 )
```

## Hamming Distance
```{r}
# Convert true/false to 1s and 0s
test_complete_games$turker_label <- as.logical(test_complete_games$turker_label)
test_complete_games$turker_label[test_complete_games$turker_label == "true"] <- 1
test_complete_games$turker_label[test_complete_games$turker_label == "false"] <- 0

complete_all_games_wide <- test_complete_games %>%
  select(role, stim_num, rule_idx, gameid, turker_label) %>%
  spread(role, turker_label) %>%
  mutate(rule_type = floor(rule_idx/10))

# Compute Hamming Distances for Concepts
hamming_distances <- complete_all_games_wide %>%
  group_by(rule_idx, gameid) %>%
  summarize(d = sum(explorer != student)) %>%
  mutate(rule_type = floor(rule_idx/10), Distribution="Empirical") 

hamming_distances$rule_idx <- as.factor(hamming_distances$rule_idx)
hamming_distances$rule_type <- as.factor(hamming_distances$rule_type)
hamming_distances <- hamming_distances %>%
    mutate(rule_type_text = 
           fct_recode(rule_type,
              "Single " = "0",
              "Conj." = "1",
              "Disj." = "2",
              "Conj. Disj." = "3",
              "Disj. Conj." = "4"
            )
    )

# Mean Hamming Distance of True Pairs
mean(hamming_distances$d)
```


```{r}
# Comparing teacher average accuracy vs. average hamming distance for concepts
comparison_acc_hd <- hamming_distances %>%
  group_by(rule_idx) %>%
  summarise(mean_d = mean(d)) %>%
  inner_join(complete_test_summary) %>%
  mutate(rule_type_text = 
           fct_recode(rule_type,
              "Single " = "0",
              "Conj." = "1",
              "Disj." = "2",
              "Conj. Disj." = "3",
              "Disj. Conj." = "4"
            )
    )

cor.test(comparison_acc_hd$explorer_acc, comparison_acc_hd$mean_d)

ggplot(comparison_acc_hd
       , aes(x=explorer_acc, y=mean_d, fill=rule_type_text)) +
  geom_point(size = 5, shape=21, color="black") +
  theme_few() +
  guides(fill = guide_legend("Rule"), color=FALSE) +
  labs(
    x = "Average Teacher Accuracy",
    y = "Average Hamming Distance"
  ) +
  theme(
    axis.title = element_text(size=15),
    legend.title = element_text(size=15),
    legend.text = element_text(size=10),
    plot.title = element_blank(),
    legend.position = c(0.85, 0.75),
    legend.background = element_rect(fill=alpha(0.1)),
  )
ggsave("./analyses/dist-by-acc.png", plot = last_plot(), width = 5, height = 4, dpi = 300 )
```

```{r}
combo_plot <- plot_grid(plot.miss_rate, plot.fp_rate, labels = c("a", "b"), nrow = 2, align = "v")
combo_plot
#ggsave("./analyses/concept-type-mr-fpr.png", plot = combo_plot, width = 5, height = 5, dpi = 300, )
```
# Compute 95 confidence interval and mean for dataframe of mean hamming distances
get_hd_stats<- function(x) {
  x <- x[order(-x$mean_d),]
  result <- list("lower_ci" = x[94, "mean_d"], "upper_ci" = x[6, "mean_d"], "mean"=mean(x$mean_d), x)
  return(result)
}


```{r}
# Permute teach-student pairs within a concept
# and take the overall mean hamming distance.
compute_average_intra_concept_shuffle_hd <- function() {
  df <- data.frame()
  for (i in 0:49) {
    x <- test_complete_games %>%
      filter(rule_idx == i) %>%
      group_by(role, gameid) %>%
      summarise(labels = paste(turker_label, collapse=", ")) %>%
      spread(role, labels)
    x$explorer <- sample(x$explorer)
    x <- x %>%
      mutate(
        explorer = strsplit(x$explorer, split = ","),
        student = strsplit(x$student, split = ","),
        d = 0
      ) 
    x$explorer = lapply(x$explorer, as.numeric)
    x$student = lapply(x$student, as.numeric)
    
    for (row in 1:nrow(x)) {
        x[row, "d"] = sum(x$explorer[[row]] != x$student[[row]])
    }
    df <- bind_rows(df, x)
  }
  result <- data.frame("Distribution"= "Intra-Concept Shuffled", "mean_d"=0)
  result$mean_d = mean(df$d)
  return (result)
}

concept_shuffled_hd <- data.frame()
for (i in 1:100) {
  concept_shuffled_hd <- bind_rows(concept_shuffled_hd, compute_average_intra_concept_shuffle_hd())
}


concept_shuffled_hd_stats <- get_hd_stats(concept_shuffled_hd)
View(concept_shuffled_hd_stats)
```

```{r}
# Permute teacher-student pairs across entire dataset
# and take the overall mean hamming distance.
compute_average_random_shuffle_hd <- function() {
  df <- data.frame()
  for (i in 0:49) {
    x <- test_complete_games %>%
      group_by(role, gameid, rule_idx) %>%
      summarise(labels = paste(turker_label, collapse=", ")) %>%
      spread(role, labels)
    
    x$explorer <- sample(x$explorer)
    x <- x %>%
      mutate(
        d = 0
      )
    x$explorer = strsplit(x$explorer, split = ",")
    x$student = strsplit(x$student, split = ",")
    x$explorer = lapply(x$explorer, as.numeric)
    x$student = lapply(x$student, as.numeric)
    
    for (row in 1:nrow(x)) {
        x[row, "d"] = sum(x$explorer[[row]] != x$student[[row]])
    }
    df <- bind_rows(df, x)
  }
  result <- data.frame("Distribution"= "Randomly Shuffled", "mean_d"=0)
  result$mean_d = mean(df$d)
  return (result)
}

random_shuffle_hd <- data.frame()
for (i in 1:100) {
  random_shuffle_hd <- bind_rows(random_shuffle_hd, compute_average_random_shuffle_hd())
  print(i)
}

random_shuffle_hd_stats <- get_hd_stats(random_shuffle_hd)
View(random_shuffle_hd_stats)
```

```{r}
# Permute teacher-student pairs across rules
# and take the overall mean hamming distance.
compute_average_rule_shuffle_hd <- function() {
  df <- data.frame()
  for (i in 0:4) {
    x <- test_complete_games %>%
      mutate(rule_type = floor(rule_idx/10)) %>%
      filter(rule_type == i) %>%
      group_by(role, gameid, rule_idx) %>%
      summarise(labels = paste(turker_label, collapse=", ")) %>%
      spread(role, labels)
    
    x$explorer <- sample(x$explorer)
    x <- x %>%
      mutate(
        d = 0
      )
    x$explorer = strsplit(x$explorer, split = ",")
    x$student = strsplit(x$student, split = ",")
    x$explorer = lapply(x$explorer, as.numeric)
    x$student = lapply(x$student, as.numeric)
    
    for (row in 1:nrow(x)) {
        x[row, "d"] = sum(x$explorer[[row]] != x$student[[row]])
    }
    df <- bind_rows(df, x)
  }
  result <- data.frame("Distribution"= "Intra-Rule Shuffled", "mean_d"=0)
  result$mean_d = mean(df$d)
  return (result)
}

rule_shuffle_hd <- data.frame()
for (i in 1:100) {
  rule_shuffle_hd <- bind_rows(rule_shuffle_hd, compute_average_rule_shuffle_hd())
  print(i)
}

rule_shuffle_hd_stats <- get_hd_stats(rule_shuffle_hd)
View(rule_shuffle_hd_stats)
```


## Language Analysis
```{r}
# Load Chat Messages
temp <- list.files(
    "../../../data/mp-game-6/complete_games/chatMessage",
  pattern="*.tsv",
  full.names=TRUE
)

msgs_complete_games <-do.call(rbind, lapply(temp, readr::read_tsv)) %>%
  group_by(gameid)
```

```{r}
msgs_complete_games$messageType <- as.factor(msgs_complete_games$messageType)
msgs_complete_games$uttClass <- as.factor(msgs_complete_games$uttClass)

msgs_complete_games <- msgs_complete_games %>% mutate(rule_type = floor(rule_idx/10))
msgs_complete_games$rule_type <- as.factor(msgs_complete_games$rule_type)


msgs_complete_games <- msgs_complete_games %>%  
  mutate(messageTypeText = fct_recode(messageType,
    "Confirmation" = "C",
    "Follow Up" = "F",
    "Informative" = "I",
    "Misc." = "M",
    "Social" = "S"
  )) %>%
  mutate(uttClassText = fct_recode(uttClass,
    "Generics" = "G",
    "Quantifiers" = "Q",
    "Adverbials" = "P",
    "Y/N" = "A",
    "Logic" = "L",
    "Either-Or" = "EO",
    "Conditionals" = "C",
    "Other" = "O",
    "Numerics" = "N",
    "Exemplars" = "E",
    "Imperatives" = "I",
    "Questions" = "?")) %>%
    mutate(rule_type_text = fct_recode(rule_type,
    "Single" = "0",
    "Conj." = "1",
    "Disj." = "2",
    "Conj. Disj." = "3",
    "Disj. Conj." = "4"
))

```

```{r}
ggplot(msgs_complete_games, aes(messageTypeText)) + 
  labs(
    x = "Message Type",
    y = "# of Messages"
  ) + geom_bar()
```

```{r}
explorer_msg_counts <- msgs_complete_games %>%
  filter(role == "explorer") %>% 
  subset(uttClassText != "NA")%>%
  subset(uttClassText != "Logic") %>%
  subset(uttClassText != "Either-Or") %>%  
  group_by(uttClassText) %>%
  tally() %>%
  transform(uttClassText = reorder(uttClassText, -n))

ggplot(explorer_msg_counts, aes(x = uttClassText, y = n)) + 
  labs(
    x = "",
    y = "# of Messages", 
    title = ""
  ) + geom_col() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size=15),
    axis.text.y = element_text(size=15),
    axis.title.y = element_text(size=18)
    )

ggsave("./analyses/teacher-langauge.png", plot = last_plot(), dpi = 300)
```

```{r}
explorer_msg_counts <- msgs_complete_games %>%
  filter(role == "explorer") %>% 
  subset(uttClassText != "NA")%>%
  group_by(uttClassText, rule_type_text) %>%
  tally() %>%
  transform(uttClassText = reorder(uttClassText, -n))

sum_explorer_msg_counts <- explorer_msg_counts %>%
  group_by(rule_type_text) %>%
  summarize(total = sum(n)) 

explorer_msg_counts_percentages <- explorer_msg_counts %>%
  inner_join(sum_explorer_msg_counts) %>%
  mutate(percentage = (n/total * 100))

ggplot(explorer_msg_counts_percentages, aes(x = uttClassText, y = percentage)) + 
  labs(
    x = "Language Type",
    y = "% of Messages", 
    title = "Teacher: Language Usage Across Informative & Follow-Up Messages"
  ) + geom_col() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_wrap(~rule_type_text, 1)

ggsave("./analyses/teacher-langauge-facet.png", plot = last_plot(), dpi = 300)
```


```{r}
student_msg_counts <- msgs_complete_games %>%
  filter(role == "student") %>% 
  subset(uttClassText != "NA")%>%
  group_by(uttClassText) %>%
  tally() %>%
  transform(uttClassText = reorder(uttClassText, -n))

ggplot(student_msg_counts, aes(x = uttClassText, y = n)) + 
  labs(
    x = "Language Type",
    y = "# of Messages", 
    title = "Student: Language Usage Across Informative & Follow-Up Messages"
  ) + geom_col() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Timing Analysis -- Entire Chat Duration

```{r regression_time}
df.time <- data.frame(bind_rows(
  msgs_complete_games %>%
    group_by(gameid, rule_idx) %>%
    summarize(learnTime = sum(reactionTime)) %>%
    mutate(role = 'student'),
  time_complete_games %>%
    filter(role == "explorer") %>%
    select(role, gameid, rule_idx, train) %>%
    rename(learnTime = train)
)) %>%
  mutate(
    rule_type = floor(rule_idx/10),
    workerid = paste(gameid, role, sep = "_"),
    rule_fac = factor(rule_type,
                     levels = c(0, 1, 2, 3, 4),
                     labels = c("single","conj", "disj",
                                "conjDisj", "disjConj")),
   concept_fac = as.factor(as.character(rule_idx)),
   role = as.factor(as.character(role))
)


contrasts(df.time$rule_fac) = contr.sum(5)
#contrasts(df.time$role) = contr.sum(2) 
contrasts(df.time$role)
contrasts(df.time$rule_fac) 

brm.time.rs <- brm(
  data = df.time,
  formula = learnTime  ~ rule_fac*role + 
    (1 + rule_fac | workerid) +
    (1 + role | concept_fac),
  family = "shifted_lognormal",
  chains = 3, cores = 3
)

ggplot(df.time, aes( x = log(learnTime)))+
  geom_histogram()

summary(brm.time.rs)
```

```{r reg_time_pp}
## this is all to generate "posterior predictives" dropping out the random effects
## this is used to estimate the size of the effect in the "data space" (e.g., seconds)
newdata = expand.grid(rule_fac = factor(
  levels(df.time$rule_fac),
    levels = c("single","conj", "disj", "conjDisj", "disjConj")),
  role = factor(levels(df.time$role))) 

fit.time = as.data.frame(fitted( brm.time.rs,
                          newdata = newdata, re_formula = NA, 
                          summary = FALSE # extract the full MCMC
))

colnames(fit.time) = newdata %>% 
  mutate(newcol = paste(rule_fac, role, sep = "_")) %>% 
  pull(newcol)

posterior.predictive.fit.time <- fit.time %>%
  mutate(stud_minus_teach = (
    (single_student - single_explorer) +
           (conj_student - conj_explorer) + 
           (disj_student - disj_explorer) + 
           (conjDisj_student - conjDisj_explorer) + 
           (disjConj_student - disjConj_explorer)
           ) / 5,
    stud_minus_teach_prob = stud_minus_teach )

# generate 95% credible intervals
quantile(posterior.predictive.fit.time$stud_minus_teach_prob, probs = c(.5, .025, .975))

posterior.predictive.fit %>%
  ggplot(., aes( x = stud_minus_teach_prob))+
  geom_histogram()
```
```{r eval = F}
# model variant where we "center" the role
# so we look at the main effect of concepts  at the average value between teacher and student
# dont think this is that interesting for this analysis
contrasts(df.time$rule_fac) = contr.sum(5)
contrasts(df.time$role) = contr.sum(2)
contrasts(df.time$role)
contrasts(df.time$rule_fac)

brm.time.rs.centerBoth <- brm(
  data = df.time,
  formula = learnTime  ~ rule_fac*role + 
    (1 + rule_fac | workerid) +
    (1 + role | concept_fac),
  family = "shifted_lognormal",
  chains = 3, cores = 3
)
summary(brm.time.rs.centerBoth)
```


```{r}
complete_games_avg_chat_times <- msgs_complete_games %>%
  group_by(gameid, rule_idx) %>%
  summarize(chatTime = sum(reactionTime)) %>%
  mutate(rule_type = floor(rule_idx/10)) %>%
  group_by(rule_type, rule_idx) %>%
  tidyboot_mean(col=chatTime) %>%
  mutate(Learning="Language")

complete_games_avg_train_times <- time_complete_games %>%
  filter(role == "explorer") %>%
  group_by(rule_idx) %>%
  tidyboot_mean(col=train) %>%
  mutate(Learning="Observation", rule_type = floor(rule_idx/10))

complete_games_avg_times <- complete_games_avg_chat_times %>%
  bind_rows(complete_games_avg_train_times)

complete_games_avg_times$rule_idx <- as.factor(complete_games_avg_times$rule_idx)
complete_games_avg_times$rule_type <- as.factor(complete_games_avg_times$rule_type)
complete_games_avg_times$Learning <- as.factor(complete_games_avg_times$Learning)


complete_games_avg_times <- complete_games_avg_times %>%
  mutate(rule_type_text = fct_recode(rule_type,
    "Single" = "0",
    "Conj." = "1",
    "Disj." = "2",
    "Conj. Disj." = "3",
    "Disj. Conj." = "4"
  )) %>%
  mutate(Learning = 
           factor(Learning, levels = c("Observation", "Language")
  ))
```

```{r}
ggplot() + 
geom_linerange(data=complete_games_avg_times, mapping=aes(x=Learning, ymin=ci_lower, ymax=ci_upper), width=0.2, size=1) + 
geom_point(data=complete_games_avg_times, mapping=aes(x=Learning, y=empirical_stat), size=4, shape=21, fill="white") +
theme_few() + 
facet_wrap(~rule_type_text, 1) +
  labs(
    title = "Time Analysis: Learning from Observation vs. Language (Entire Chat)",
    x = "Game Phase",
    y = "Time (Seconds)"
  )
```

## Timing Analysis -- Informative Chat Duration
```{r}
complete_games_avg_chat_times <- msgs_complete_games %>%
  filter(messageType == 'I' | messageType == 'F') %>%
  group_by(gameid, rule_idx) %>%
  summarize(chatTime = sum(reactionTime)) %>%
  mutate(rule_type = floor(rule_idx/10)) %>%
  group_by(rule_type, rule_idx) %>%
  tidyboot_mean(col=chatTime) %>%
  mutate(Learning="Language")

complete_games_avg_train_times <- time_complete_games %>%
  filter(role == "explorer") %>%
  group_by(rule_idx) %>%
  tidyboot_mean(col=train) %>%
  mutate(Learning="Observation", rule_type = floor(rule_idx/10))

complete_games_avg_times <- complete_games_avg_train_times %>%
  bind_rows(complete_games_avg_chat_times)

complete_games_avg_times$rule_idx <- as.factor(complete_games_avg_times$rule_idx)
complete_games_avg_times$rule_type <- as.factor(complete_games_avg_times$rule_type)
complete_games_avg_times$Learning <- as.factor(complete_games_avg_times$Learning)


complete_games_avg_times <- complete_games_avg_times %>%
  mutate(rule_type_text = fct_recode(rule_type,
    "Single" = "0",
    "Conj." = "1",
    "Disj." = "2",
    "Conj. Disj." = "3",
    "Disj. Conj." = "4"
  )) %>%
  mutate(Learning = 
           factor(Learning, levels = c("Observation", "Language")
  ))
```

```{r}
ggplot() + 
geom_errorbar(data=complete_games_avg_times, mapping=aes(x=Learning, ymin=ci_lower, ymax=ci_upper), size=0.2, width=0.2,
               position = position_dodge(width=2, preserve = "total")) +
geom_point(data=complete_games_avg_times, mapping=aes(x=Learning, y=empirical_stat), size=4, shape=21, fill="white") +
geom_line(data=complete_games_avg_times, aes(x=Learning, y=empirical_stat, group=rule_idx)) +
theme_few() + 
facet_wrap(~rule_type_text, 1) +
  labs(
    x = "",
    y = "Average Time (Seconds)" 
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("./analyses/time.png", plot = last_plot(), width = 5, height = 3, dpi = 300)
```

